\addcontentsline{toc}{chapter}{บรรณานุกรม}

\bibliographystyle{plain}


\begin{thebibliography}{}
	
	\bibitem{ref:rof-inpaint-chan-shen} 
	T.F. Chan and J. Shen , “Mathematical models of local non-texture inpaintings”, SIAM Journal on Applied Mathematics, vol. 62, no. 3, pp. 1019–1043, 2001. 
	%\url{http://www.jstor.org/stable/3061798}
	
	\bibitem{ref:ROF-template} 
	L. I. Rudin, S. Osher, E. Fatemi, “Nonlinear total variation based noise removal algorithms", Physica D: Nonlinear Phenomena, vol 60, issues 1–4, pp. 259-268, 1992. 
	%\url{https://doi.org/10.1016/0167-2789(92)90242-F}
	
	\bibitem{ref:FixpointSolver}
	C.R. Vogel and M.E. Oman,“Iterative methods for total variation denoising", SIAM Journal on Scientific Computing. vol. 17, pp. 227-238, 1996.
	
	\bibitem{ref:splitbergman-inpaint}
	T. Goldstein and S. Osher,“The Split Bregman Method for L1-Regularized Problems", SIAM Journal on Imaging Sciences. vol. 2, issue 2, pp. 323-343, 2009.
	
	\bibitem{ref:image-pyramid}
	E.H. Andelson and C.H. Anderson and J.R. Bergen and P.J. Burt and J.M. Ogden. "Pyramid methods in image processing". 1984
	% วิกิ บอกว่าให้ ref ของคุณ Andelson
	% doi 10.1.1.56.8646
	%\url{https://en.wikipedia.org/wiki/Pyramid_(image_processing)#cite_ref-1}
	%\url{https://en.wikipedia.org/wiki/Multiresolution_analysis}
	
	\bibitem{ref:PSNR}
	David Salomon. Data Compression: The Complete Reference (4 ed.). Springer. pp. 281. 2007.
	%ISBN 978-1846286025.  \url{https://books.google.co.th/books?id=ujnQogzx_2EC&lpg=PA281&ots=FolwqB8qsN&dq=PSNR+infinite&pg=PA281&redir_esc=y#v=onepage&q=PSNR%20infinite&f=false}
	
	\bibitem{ref:SSIM}
	Zhou Wang, Alan Conrad Bovik, Hamid Rahim Sheikh and Eero P. Simoncelli, "Image quality assessment: from error visibility to structural similarity," in IEEE Transactions on Image Processing, vol. 13, no. 4, pp. 600-612, 2004.
	%\url{https://doi.org/10.1109/TIP.2003.819861}

	\bibitem{ref:regularization}
	A. N. Tikhonov and V. Y. Arsenin. Solutions of Ill-posed Problems. Wiston and Sons, Washington, D.C., 1977

	\bibitem{ref:calculus_of_variation}
	B. Dacorogna. Introduction to the Calculus of Varations. Introduction to the Calculus of Varations, 2004.

	\bibitem{ref:general_functional_stationary}
	N. Chumchob. A study of effective variational models and efficient numerical methods for image registration. University of Liverpool, UK 2010

\end{thebibliography}
\clearpage